# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
The data in activity.csv file is loaded into r data frame. 
```{r, echo=TRUE}
   #load the data from file 'activity.csv'
   activity <- read.csv('activity.csv')
```
Rows with no measurements are then removed.
```{r, echo=TRUE}
   #remove the rows with no measurements i.e. NA
   activity.clean <- na.omit(activity)
   
```
Out of total `r dim(activity)[1]` rows in the data file, `r dim(activity.clean)[1]` rows were found to be complete (i.e. having some value other than NA).

## What is mean total number of steps taken per day?

Total number of steps taken per day is calculated as follows
```{r, echo=TRUE}
   activity.daily <- aggregate(steps~date,activity,sum)
```

Histogram of total steps taken per day
```{r, echo=TRUE}
   hist(activity.daily$steps,xlab = 'Total Steps per Day',main = 'Histogram of Total Steps per Day')
```

Mean steps taken per day are 
```{r, echo=TRUE}
   mean(activity.daily$steps)
```

Median steps taken per day are 
```{r, echo=TRUE}
   median(activity.daily$steps)
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
