# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
The data in activity.csv file is loaded into r data frame. 
```{r, echo=TRUE}
   #load the data from file 'activity.csv'
   activity <- read.csv('activity.csv')
```
Rows with no measurements are then removed.
```{r, echo=TRUE}
   #remove the rows with no measurements i.e. NA
   activity.clean <- na.omit(activity)
   
```
Out of total `r dim(activity)[1]` rows in the data file, `r dim(activity.clean)[1]` rows were found to be complete (i.e. having some value other than NA).

## What is mean total number of steps taken per day?

Total number of steps taken per day is calculated as follows
```{r, echo=TRUE}
   activity.daily <- aggregate(steps~date,activity,sum)
```

Histogram of total steps taken per day
```{r, echo=TRUE}
   hist(activity.daily$steps,xlab = 'Total Steps per Day',main = 'Histogram of Total Steps per Day')
```

Mean steps taken per day are 
```{r, echo=TRUE}
   mean(activity.daily$steps)
```

Median steps taken per day are 
```{r, echo=TRUE}
   median(activity.daily$steps)
```


## What is the average daily activity pattern?

Average steps taken within each time interval (across all days)
```{r,echo=TRUE}
    activity.time <- aggregate(steps~interval,activity.clean,mean)
```

Time series plot
```{r,echo=TRUE}
   plot(x=activity.time$interval,y=activity.time$steps,type = 'l',xlab = 'Time Interval',ylab = 'Average Number of Steps')
```

Time interval for which maximum steps are taken
```{r,echo=TRUE}
   activity.max <- activity.time[activity.time$steps==max(activity.time$steps),]
   activity.max
```

## Imputing missing values

Total number of missing values (i.e. rows with NA) are
```{r,echo=TRUE}
   dim(activity)[1] - dim(activity.clean)[1]
```

Impute missing values using the interval average steps
```{r,echo=TRUE}
   activity.imputed <- activity
   activity.imputed <- transform(activity.imputed, 
                                 steps=ifelse(is.na(steps),
                                              activity.time[activity.time$interval %in% interval,'steps'],
                                              steps))

```

Total number of steps taken per day is calculated as follows
```{r, echo=TRUE}
   activity.imputed.daily <- aggregate(steps~date,activity.imputed,sum)
```

Histogram of total steps taken per day
```{r, echo=TRUE}
   hist(activity.imputed.daily$steps,xlab = 'Total Steps per Day',main = 'Histogram of Total Steps per Day')
```

Mean steps taken per day are 
```{r, echo=TRUE}
   mean(activity.imputed.daily$steps)
```

Median steps taken per day are 
```{r, echo=TRUE}
   median(activity.imputed.daily$steps)
```

With imputation, median has converged to mean i.e. mean and median are now same.

## Are there differences in activity patterns between weekdays and weekends?
